17th International Satisfiability Modulo Theories Competition (SMT-COMP 2022): Rules and Procedures

### 2022-02-01 rules/rules22.tex
new rules

\title{15th International Satisfiability Modulo Theories Competition
  (SMT-COMP 2021): Rules and Procedures}

@@

\author{%
Haniel Barbosa\\
Universidade Federal de Minas Gerais\\
Brazil\\
{\small\href{mailto:hbarbosa@dcc.ufmg.br}{\texttt{hbarbosa@dcc.ufmg.br}}}\\
\and
Jochen Hoenicke (chair)\\
Universit\"at Freiburg\\
Germany\\
{\small\href{mailto:hoenicke@informatik.uni-freiburg.de}{\texttt{hoenicke@informatik.uni-freiburg.de}}}\\
\and
Antti Hyvarinen\\
Universita della Svizzera italiana \\
Switzerland \\
{\small\href{mailto:antti.hyvaerinen@usi.ch}{\texttt{antti.hyvaerinen@usi.ch}}} \\
}

@@

\begin{description}
\item[March~15] Deadline for new benchmark contributions.
\item[May~7] Final versions of competition tools (e.g., benchmark
  scrambler) are made available.  Benchmark libraries are frozen.
\item[May~30] Deadline for first versions of solvers (for all tracks),
  including information about which tracks and divisions are being
  entered, and magic numbers for benchmark scrambling.
\item[June~13] Deadline for final versions of solvers, including
  system descriptions.
\item[June~15] Opening value of NYSE Composite Index used to compute
  random seed for competition tools.
\item[July~18/19] SMT Workshop; end of competition, presentation of
  results.
\end{description}

@@

SMT-COMP~2021 is part of the SMT Workshop~2021
(\url{http://smt-workshop.cs.uiowa.edu/2021/}),
which is affiliated with CAV~2021 (\url{http://i-cav.org/2021/}).
The SMT Workshop will include a block of time to present the results of the
competition.
%
Accordingly, researchers are highly encouraged to submit both new
benchmarks and new or improved solvers to raise the level of
competition and advance the state-of-the-art in automated SMT problem
solving.

SMT-COMP 2021 will have four tracks: the \maintrack (before 2019: Main Track),
the \inctrack (before 2019: Application Track), the \ucoretrack, and the
\mvaltrack.  In addition there will be two experimental tracks sponsored
by AWS: the \paralleltrack{} and the \cloudtrack{}.
%
Within each track there are multiple divisions, where each division
uses benchmarks from a specific group of SMT-LIB logics.
We will recognize winners as measured by number of benchmarks solved
(taking into account the weighting detailed in
Section~\ref{sec:scoring}); we will also recognize solvers based on
additional criteria.

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Liana Hadarean,
  Matthias Heizmann, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
  and Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2021.
%
As in previous years, we have revised the rules slightly.  Some rule
changes in 2021 are designed to not overly punish solvers producing
syntactically wrong output, by treating those outputs as unknown and
not as unsoundness.  Moreover, we added more divisions to the model
validation track.
%
The principal changes from the previous competition rules are the following:
\begin{itemize}
  \item {\bf Divisions now may contain more than one logic.} Previously, every
  division was comprised of a single logic. There are currently over 60 logics
  in SMT-LIB, which makes a short summary of the results impossible.  On the
  other hand the competition-wide scoring does a comparison between solvers that
  cannot be sensibly compared as they support completely disjoint logics. To get
  a better overview, this year divisions will combine related logics, thus
  reducing the number of divisions and obtaining more manageable and meaningful
  results.  Rather than logics, solvers will declare the divisions they
  enter. They will be ranked by the number of benchmarks they solve across all
  logics in the divisions entered.
  \begin{itemize}
    \item Quantifier-free divisions:
    \begin{itemize}
      \item QF\_Equality\\
Logics: QF\_UF, QF\_AX, QF\_DT, QF\_UFDT
\item QF\_Equality+LinearArith\\
Logics: QF\_ALIA, QF\_AUFLIA, QF\_UFLIA, QF\_UFLRA, QF\_UFIDL
\item QF\_Equality+NonLinearArith\\
Logics: QF\_UFNRA, QF\_UFNIA, QF\_ANIA, QF\_AUFNIA
\item QF\_Equality+Bitvec\\
Logics: QF\_ABV, QF\_UFBV, QF\_AUFBV
\item QF\_Equality+Bitvec+Arith\\
Logics: QF\_AUFBVLIA, QF\_AUFBVNIA, QF\_UFBVLIA
\item QF\_LinearIntArith\\
Logics: QF\_LIA, QF\_LIRA, QF\_IDL
\item QF\_LinearRealArith\\
Logics: QF\_LRA, QF\_RDL
\item QF\_Bitvec\\
Logics: QF\_BV
\item QF\_FPArith\\
Logics: QF\_FP, QF\_UFFP, QF\_FPLRA, QF\_BVFP, QF\_ABVFP, QF\_AUFBVFP, QF\_BVFPLRA, QF\_ABVFPLRA
\item QF\_NonLinearIntArith\\
Logics: QF\_NIA, QF\_NIRA
\item QF\_NonLinearRealArith\\
Logics: QF\_NRA
\item QF\_Strings\\
Logics: QF\_S, QF\_SLIA, QF\_SNIA

@@

SMT-COMP entrants must be submitted via StarExec (solvers), or
communicated separately to the organisers for the \paralleltrack{} and
\cloudtrack{}, \emph{and}
the above web form (accompanying information) until the end of
{\bf May~30, 2021} anywhere on earth.
After this date \emph{no new entrants} will be accepted.
However, updates to existing entrants on StarExec or \paralleltrack{}
and \cloudtrack{}
will be accepted until the end of {\bf June~13, 2021} anywhere on earth.

@@

\header{Dates of Competition.}
%
The bulk of the computation will take place during the weeks leading
up to SMT 2021.  Intermediate results will be regularly posted to the
SMT-COMP website as the competition runs.
%
The organizers reserve the right to prioritize certain competition
tracks or divisions to ensure their timely completion, and in
exceptional circumstances to complete divisions after the SMT
Workshop.

@@

The limits for \paralleltrack{} and \cloudtrack{} are available at
\url{https://smt-comp.github.io/2021/parallel-and-cloud-tracks.html}.

@@

\header{New benchmarks.}
The deadline for submission of new benchmarks was {\bf March~15, 2021}.
The organizers, in collaboration with the SMT-LIB maintainers, will be
checking and curating these until {\bf May~7, 2021}.  The SMT-LIB
maintainers intend to make a new release of the benchmark library
publicly available on or close to this date.

@@

SMT-COMP 2021 is organized under the direction of the SMT Steering
Committee. The organizing team is
%
\begin{itemize}
\setlength{\itemsep}{0pt}
\item \href{http://homepages.dcc.ufmg.br/~hbarbosa/}{Haniel Barbosa}~-- Universidade Federal de Minas Gerais, Brazil
\item \href{https://jochen-hoenicke.de/}{Jochen Hoenicke}~-- Universit\"at Freiburg, Germany (chair)
\item \href{http://www.inf.usi.ch/postdoc/hyvarinen/}{Antti Hyv\"arinen}~--
    Universit\`a della Svizzera italiana, Switzerland
\end{itemize}
%
The competition chairs are responsible for policy and procedure decisions,
such as these rules, with input from the co-organizers.

@@

\header{Disclosure.}
%
Haniel Barbosa is part of the developing teams of the SMT solvers
CVC4~\cite{cvc4-smtcomp18} and veriT~\cite{verit}.
%
Jochen Hoenicke is part of the developing team of the SMT solver
SMTInterpol~\cite{smtinterpol}.
Antti Hyvarinen is part of the developing team of the SMT solver
OpenSMT~\cite{opensmt2}.

>>>>

\title{17th International Satisfiability Modulo Theories Competition
  (SMT-COMP 2022): Rules and Procedures}

@@

\author{%
Haniel Barbosa (chair)\\
Universidade Federal de Minas Gerais\\
Brazil\\
{\small\href{mailto:hbarbosa@dcc.ufmg.br}{\texttt{hbarbosa@dcc.ufmg.br}}}\\
\and
Fran\c{c}ois Bobot\\
CEA List \\
France \\
{\small\href{mailto:Francois.BOBOT@cea.fr}{\texttt{https://github.com/bobot}}} \\
\and
Jochen Hoenicke\\
Universit\"at Freiburg\\
Germany\\
{\small\href{mailto:hoenicke@informatik.uni-freiburg.de}{\texttt{hoenicke@informatik.uni-freiburg.de}}}
}

@@

\begin{description}
\item[TDB] Deadline for new benchmark contributions.
\item[May~28] Final versions of competition tools (e.g., benchmark
  scrambler) are made available.  Benchmark libraries are frozen.
\item[June~18] Deadline for first versions of solvers (for all tracks),
  including information about which tracks and divisions are being
  entered, and magic numbers for benchmark scrambling.
\item[July~2] Deadline for final versions of solvers, including
  system descriptions.
\item[TDB] Opening value of NYSE Composite Index used to compute
  random seed for competition tools.
\item[August 11/12] SMT Workshop; end of competition, presentation of
  results.
\end{description}

@@

SMT-COMP~2022 is part of the SMT Workshop~2022
(\url{http://smt-workshop.cs.uiowa.edu/2022/}) \hb{check},
which is affiliated with IJCAR~2022 (\url{https://easychair.org/smart-program/IJCAR2022/}).
The SMT Workshop will include a block of time to present the results of the
competition.
%
Accordingly, researchers are highly encouraged to submit both new
benchmarks and new or improved solvers to raise the level of
competition and advance the state of the art in automated SMT problem
solving.

SMT-COMP 2022 will have five \hb{check} tracks: the \maintrack (before 2019: Main Track),
the \inctrack (before 2019: Application Track), the \ucoretrack, and the
\mvaltrack.  In addition there will be two experimental tracks sponsored
by AWS: the \paralleltrack{} and the \cloudtrack{}.
%
Within each track there are multiple divisions, where each division
uses benchmarks from a specific group of SMT-LIB logics.
We will recognize winners as measured by number of benchmarks solved
(taking into account the weighting detailed in
Section~\ref{sec:scoring}); we will also recognize solvers based on
additional criteria.

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Liana Hadarean,
  Matthias Heizmann, Antti Hyvarinen, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
  and Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2022.
%

\hb{change more from here}
As in previous years, we have revised the rules slightly.  Some rule
changes in 2021 are designed to not overly punish solvers producing
syntactically wrong output, by treating those outputs as unknown and
not as unsoundness.  Moreover, we added more divisions to the model
validation track.
%
The principal changes from the previous competition rules are the following:
\begin{itemize}
  \item {\bf Divisions now may contain more than one logic.} Previously, every
  division was comprised of a single logic. There are currently over 60 logics
  in SMT-LIB, which makes a short summary of the results impossible.  On the
  other hand the competition-wide scoring does a comparison between solvers that
  cannot be sensibly compared as they support completely disjoint logics. To get
  a better overview, this year divisions will combine related logics, thus
  reducing the number of divisions and obtaining more manageable and meaningful
  results.  Rather than logics, solvers will declare the divisions they
  enter. They will be ranked by the number of benchmarks they solve across all
  logics in the divisions entered.
  \begin{itemize}
    \item Quantifier-free divisions:
    \begin{itemize}
      \item QF\_Equality\\
Logics: QF\_UF, QF\_AX, QF\_DT, QF\_UFDT
\item QF\_Equality+LinearArith\\
Logics: QF\_ALIA, QF\_AUFLIA, QF\_UFLIA, QF\_UFLRA, QF\_UFIDL
\item QF\_Equality+NonLinearArith\\
Logics: QF\_UFNRA, QF\_UFNIA, QF\_ANIA, QF\_AUFNIA
\item QF\_Equality+Bitvec\\
Logics: QF\_ABV, QF\_UFBV, QF\_AUFBV
\item QF\_Equality+Bitvec+Arith\\
Logics: QF\_AUFBVLIA, QF\_AUFBVNIA, QF\_UFBVLIA
\item QF\_LinearIntArith\\
Logics: QF\_LIA, QF\_LIRA, QF\_IDL
\item QF\_LinearRealArith\\
Logics: QF\_LRA, QF\_RDL
\item QF\_Bitvec\\
Logics: QF\_BV
\item QF\_FPArith\\
Logics: QF\_FP, QF\_UFFP, QF\_FPLRA, QF\_BVFP, QF\_ABVFP, QF\_AUFBVFP, QF\_BVFPLRA, QF\_ABVFPLRA
\item QF\_NonLinearIntArith\\
Logics: QF\_NIA, QF\_NIRA
\item QF\_NonLinearRealArith\\
Logics: QF\_NRA
\item QF\_Strings\\
Logics: QF\_S, QF\_SLIA, QF\_SNIA

@@

SMT-COMP entrants must be submitted via StarExec (solvers), or
communicated separately to the organisers for the \paralleltrack{} and
\cloudtrack{}, \emph{and}
the above web form (accompanying information) until the end of
{\bf June~18, 2022} anywhere on earth.
After this date \emph{no new entrants} will be accepted.
However, updates to existing entrants on StarExec or \paralleltrack{}
and \cloudtrack{}
will be accepted until the end of {\bf July~2, 2022} anywhere on earth.

@@

\header{Dates of Competition.}
%
The bulk of the computation will take place during the weeks leading
up to SMT 2022.  Intermediate results will be regularly posted to the
SMT-COMP website as the competition runs.
%
The organizers reserve the right to prioritize certain competition
tracks or divisions to ensure their timely completion, and in
exceptional circumstances to complete divisions after the SMT
Workshop.

@@

The limits for \paralleltrack{} and \cloudtrack{} are available at \hb{check}
\url{https://smt-comp.github.io/2021/parallel-and-cloud-tracks.html}.

@@

\header{New benchmarks.}
The deadline for submission of new benchmarks was {\bf March~15, 2021}
\hb{update when we have date}.
%
The organizers, in collaboration with the SMT-LIB maintainers, will be
checking and curating these until {\bf June~18, 2022}.

The SMT-LIB
maintainers intend to make a new release of the benchmark library
publicly available on or close to this date.

@@

SMT-COMP 2022 is organized under the direction of the SMT Steering
Committee. The organizing team is
%
\begin{itemize}
\setlength{\itemsep}{0pt}
\item \href{http://homepages.dcc.ufmg.br/~hbarbosa/}{Haniel Barbosa}~--
Universidade Federal de Minas Gerais, Brazil (chair)
\item \href{https://github.com/bobot}{Fran\c{c}ois Bobot}~-- CEA List, France
\item \href{https://jochen-hoenicke.de/}{Jochen Hoenicke}~-- Universit\"at Freiburg, Germany
\end{itemize}
%
The competition chairs are responsible for policy and procedure decisions,
such as these rules, with input from the co-organizers.

@@

\header{Disclosure.}
%
Haniel Barbosa is part of the developing teams of the SMT solvers
cvc5~\cite{cvc4-smtcomp18} and veriT~\cite{verit}.
%
Fran\c{c}ois is part of the developing team of the SMT solver COLIBRI~\cite{colibri}.
%
Jochen Hoenicke is part of the developing team of the SMT solver
SMTInterpol~\cite{smtinterpol}.
